The Accuracy of KNN, SVM, SVDD, neural network and DBSCAN, k-means for Determining the Cancer by Gene-expression Signatures And the Arrhythmia Types

### 2023-05-30 final/paper/main.tex
Update main.tex
add bayes related work and main process

@@

@@

\section{Contribution}
\begin{itemize}
  \item Hsieh Cheng-Han: KNN, SVM, DBSCAN, paper, ppt
  \item Hsu Ting-Hao: 
  \item Sun Shih-Yu: SVM, k-means, paper
  \item Lu Che-Yuan: 
  \item Huang Chia-Yen: 
\end{itemize}

>>>>

\bf{naive bayes classifier}: \rm{naive Bayes classifier} as its name suggest, is a machine learning method base on Bayesian 
theorem, this model will statistic each data and find all conditional probability of each event occurring if each outcome holds. 
And finally when it is asked to predict the result, the model will evaluate the data which requist provide and find the most 
likely outcome according to the conditional probability it just recorded.

@@

  When it comes to Naive Bayes classifier, Assume there are N known types. Denotes the N Bayes classifiers recognizing each
  type of known types as BC_1, BC_2, ..., BC_N. For each test data, let BC_1 determine whether it belongs to     type 1, if
  it does, mark it as type 1 and try classifying next test data, otherwise, BC_2 will determine whether it belongs to class_2
  or not, and so on. If all Bayes classifiers results false, namely, the data doesn't belong to     any known types, marks it
  as unknown type.

@@

\section{Contribution}
\begin{itemize}
  \item Hsieh Cheng-Han: KNN, SVM, DBSCAN, paper, ppt
  \item Hsu Ting-Hao: 
  \item Sun Shih-Yu: SVM, k-means, paper
  \item Lu Che-Yuan: 
  \item Huang Chia-Yen: Bayes, paper, poster
\end{itemize}
